Adolescent well-being in the digital age

### 2022-01-28 00-clean.qmd
USe more GWP age groups

# Categorize ages
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 105, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Focus on young people
gwp <- gwp %>%
  filter(age %in% c("15 to 19", "20 to 24"))
```

@@

```{r gallup-summarise}
gwp <- gwp %>%
  # Aggregate internet
  group_by(country, year, sex, age) %>% 
  mutate(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome, gwpi) %>%
  summarise(
    se = sd(val, na.rm = TRUE) / sqrt(n()),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

>>>>

# Categorize ages
gwp <- filter(gwp, age <= 89)
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 90, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)
```

@@

```{r gallup-summarise}
gwp <- gwp %>%
  # Aggregate internet
  group_by(country, year, sex, age) %>% 
  mutate(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome, gwpi) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```
